|

### 2020-07-23 paper.Rmd
Tweaking Sec 2.3

Eq. \ref{eq:resc} is fixed for a given input dataset, by evaluating the number of dimensions $p$ and the maximum distance from the center $R$. However, in realistic applications we may wish to trim the projected data or tune the transformation. In practice, a combination of both adjustments can be used to further zoom in on the center of the distribution, or alternatively, to soften the transformation.

@@

We therefore allow trimming of the projected observations, using $R$ as a free parameter of the display function. When selecting a value $R$ that is smaller than the maximum distance from the center, we need to ensure that the projected radius of points is always smaller than $R$ before rescaling according to Eq. \ref{eq:resc}. We do this by trimming $r_x$ as
\begin{equation}
r_x^{\mathrm{trim}} = \min(r_x, R)
\label{eq:cutR}
\end{equation}
for each observation $i = 1, ..., n$.

>>>>

The transformation in Eq. \ref{eq:resc} is fixed for a given input dataset, by evaluating the number of dimensions $p$ and the maximum distance from the center $R$. However, in realistic applications we may wish to trim the projected data or tune the transformation. In practice, a combination of both adjustments can be used to further zoom in on the center of the distribution, or alternatively, to soften the transformation.

@@

We therefore allow trimming of the projected observations, using $R$ as a free parameter of the display function. When selecting a value $R$ that is smaller than the maximum distance from the center, we need to ensure that the projected radius of points is always smaller than $R$, by trimming $r_x$ as
\begin{equation}
r_x^{\mathrm{trim}} = \min(r_x, R)
\label{eq:cutR}
\end{equation}
for each observation $x$.
